Flexibility of interactions depends on habitat suitability

### 2019-07-29 paper/manuscript.Rmd
Devictor 2010
Godsoe 2017 + Mini comment

**Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian. A better position in the grinellian niche allows for a larger Realised Eltonian niche.

@@

>>>>

**Is smaller degree a smaller Eltonian niche?** Should I frame this as the relationship between Grinellian and Eltonian. A better position in the grinellian niche allows for a larger Realised Eltonian niche. A problem of stating the hypothesis in terms of niches is that there are many definitions of niche and people is picky

*Previous state of the world: We know interactions change with the environment but we don't know beyond co-occurrence patterns*

@@

**Devictor 2010:** I can use degree to quantify realised eltonian niche

**Godsoe 2017**: Biogeographers and community ecologists have long debated the importance of biotic interactions (see Glossary) for species distributions and range limits [1–5].*But seldom the other way arround?*
